### 2017-04-27 src/algorithm.tex
latency

In this section we present an FPTAS algorithm to the VPN problem.
We are given an instance of the VPN problem 
\begin{align}
D_v = (V_v, A_v)			\\
D_p = (V_p, A_p)			\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c)	\\
c
\end{align}
For now assume all values are integral and polynomial bounded in the size of the input.
Sort the DAGs topologically and assume w.l.o.g that $s_v = s_p = 1$,
$t_v = n$, and $t_p = m$.
Let $O(i, j)$ be the optimal embedding of any $1i$ virtual path, 
into a $1j$ physical path.
We can compute $O(i, j)$ as follow:
$$
O(i, j) = \min_{a \text{ ancestor of } i} \min_{b \text{ ancestor of } j} O(a, b)
+ \min_(ai, bj)
$$
Where $\min(ai, bj)$ is the optimal embedding of a virtual 
path starting at any child of $a$, $a'$ and ending at $i$ into node $j$
that respect the bottleneck constraint, i.e. $b_d(a, a') \leg bn(b, j)$.
\todo{define bn(i, j) to be the bottleneck between i and j}
We claim that $\min(ai, bj)$ can be found efficiently 
\todo{describe how}

>>>>

In this section we present an FPTAS algorithm to the VPN problem.
We are given an instance of the VPN problem 
\begin{align}
D_v = (V_v, A_v)			\\
D_p = (V_p, A_p)			\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c)	\\
c
\end{align}
For now assume all values are integral and polynomial bounded in the size of the input.

We start with the following:
For an ancestor $a_v$ of $t'_v$ denote by $C(a_v)$ its children.
Let $a_p$ be an ancestor of $t'_p$ we want to find an embedding of minimum cost
of some virtual $c_vt'_v$-path into the node $t'_p$, 
where $c_v \in C(a_v)$.
Observe that once $c_v$ is chosen the arc $(a_v, c_v)$ determines completely
whether a physical path with a feasible bottleneck exists, namely, a physical
path exists if and only if there is a physical $s'_vt'_v$-path containing only
arcs with bandwidth at least $b_d(a_v, c_v)$.
On the other hand, the set of $c_vt'_v$-paths
determine completely the cost (and processing-wise feasibility) of the embedding.
Among all the $c_vt'_v$-paths we want to select the one that minimize the
embedding cost under the processing capacity constraints.
Figure \todo{} depicts the above observations.

\begin{figure}[ht]
\centering
\input{fig-dp}
\end{figure}

\todo{define bn(i, j) to be the bottleneck between i and j}
We claim that $\min(ai, bj)$ can be found efficiently 
\todo{describe how}

### 2017-04-27 src/latency.tex
latency

\todo{Are we going to talk about the problem also with latency constraint ?}

>>>>

\todo{Are we going to talk about the problem also with latency constraint ?}
We now extend the problem by adding a global latency constraint.
Formally, we are given a latency function $l : A_v \times A_p \to \R$,
and a latency constraint $L$.
The goal is to find a min-cost embedding that also respect the latency
constraint.
Observe that given two physical vertices $s_p$, $t_p$ and a virtual edge $e_v$
a $s_pt_p$-path that minimize the latency can be efficiently found by using any
standard shortest path algorithm where the "distance" function is replaced by
the appropriate latency.
Observe that this can also be done if we restrict ourselves to use only physical
edges with a lower bound on their bandwidth.
We now show that if all values are integral and polynomial bounded, we can
efficiently find a feasible embedding with a cost bounded by $C$ that minimize
the latency.

Let $O(t'_v, t'_p, C)$ be an embedding of some virtual $s_vt'_v$-path 
into a physical $s_pt'_p$-path that has cost not more than $C$ and that
minimizes the latency.
